Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-07-28 paper.tex
Some fixes

%\maketitle
\begin{abstract}
Embedded Systems Design requires conflicting objectives to be
optimized with an appropriate choice of hardware/software parameters. A simulation campaign guides the design in finding the best trade-offs, but, due to the big number of possible configurations, it is unfeasible to simulate all of them. For these reason Design Space Exploration (DSE) algorithms aim at finding near-optimal system configurations, only simulating a subset of them.

In this work we present PS, a new multiobjective exploration algorithm. The basic idea is to recognize \emph{interesting}, i.e. regions of the configuration space that are proving to provide better configurations w.r.t. other ones. PS evaluates more configurations in interesting regions while exploring less thoroughly the rest of the configuration space. After a detailed formal description
of the algorithm and the underlying concepts, we show a hardware/software
exploration case study. Qualitative and quantitative comparisons of PS
against a well-know multiobjective genetic approach demonstrate that,
while not outperforming it in terms of dominance, the proposed
approach can trade the uniformity and granularity qualities of the
solutions found for obtaining larger Pareto sets, thus representing a
further choice for designer when objective constrains allow it.
\end{abstract}

>>>>

%\maketitle
\begin{abstract}
Embedded Systems Design requires conflicting objectives to be
optimized with an appropriate choice of hardware/software parameters.
A simulation campaign can guide the design in finding the best
trade-offs, but due to the big number of possible configurations it
is often unfeasible to simulate all of them. For these reasons Design Space
Exploration (DSE) algorithms aim at finding near-optimal system
configurations only simulating a subset of them.

In this work we present PS, a new multiobjective exploration
algorithm. The basic idea is to recognize \emph{interesting} regions, i.e.
regions of the configuration space that are proving to provide better
configurations with regard to other ones. PS evaluates more configurations in
interesting regions while exploring less thoroughly the rest of the
configuration space. After a detailed formal description of the
algorithm and the underlying concepts, we show a 
case study involving the hardware/software exploration of a VLIW
architcture. Qualitative and quantitative comparisons of PS
against a well-know multiobjective genetic approach demonstrate that,
while not outperforming it in terms of dominance, the proposed
approach can trade the uniformity and granularity qualities of the
solutions found for obtaining larger Pareto sets, thus representing a
further choice for designer when objective constrains allow it.
\end{abstract}
